---
title: "Ab4-Ex1"
author: "Julia D"
date: "2024-11-27"
output: github_document
---
#Exercise 1
## Jane Austen Book Analysis 
This task will use the janeaustenr package to plot the most common words in the book, removing "stop words" such as a, an, and, the. 

#### Downloading the source material & necessary packages
```{r}
library(janeaustenr)
library(tidyverse)
library(stringr)
library(purrr)
library(stopwords)
```

Determining strategy/ objectives: 
1. Unstring all the words so that they can be scanned through
2. Excise all stopwords
3. Count all re-occuring words and #s of each word
4. Plot the counts 

#### Objective 1: Unstring sentances
```{r}
#Turn "senseandsensibility" into a dataset
SandS <- data.frame(sensesensibility)
typeof(SandS) 
# Now I know this is a dataframe ("list") that has 1 column the sentance. 

#I need the words of the sentence separated.
words_ss <- separate_longer_delim(SandS, "sensesensibility", delim = " ")

```

#### Objective 2: Excise the stop words & punctuation
```{r}
#Ran into issues with case down the line, so I am making sure that the stopwords are matched and removed regardless of case. Also removing punctuation, "I" and blank rows.
stopwords_list <- tolower(stopwords("en"))

filtered_SS <- words_ss %>%
  mutate(sensesensibility = tolower(trimws(sensesensibility))) %>%  
  mutate(sensesensibility = str_remove_all(sensesensibility, "[[:punct:]]")) %>%  
  filter(!sensesensibility %in% stopwords_list) %>%  
  filter(sensesensibility != "i") %>%  
  filter(sensesensibility != "") 
  

clean_data <- data.frame(word = unlist(filtered_SS))
print(clean_data)

```


#### Objective 3: Counts of the words
```{r}
word_counts <- clean_data %>%
  count(word, 
        sort = TRUE) %>%
  filter(n> 250)
print(word_counts)

```

#### Objective 4: Graph the word use
```{r} 
#graph the most used words (top 12, >250 mentions)
#Define catgories of words to colour by in graph: new column in tibble

Word_dist <- ggplot(word_counts) +
  geom_col(aes(x = word, y = n, fill= word)) +
  theme_light()

print(Word_dist)

```


